---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# idmc

<!-- badges: start -->
  [![R-CMD-check](https://github.com/OCHA-DAP/idmc/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/OCHA-DAP/idmc/actions/workflows/R-CMD-check.yaml)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The goal of idmc is to provide easy access and wrangling of displacement data
stored in the
[Internal Displacement Monitoring Centre's](https://www.internal-displacement.org)
(IDMC) displacement database. The data is retrieved from the 
[Internal Displacement Update API](https://www.internal-displacement.org/database/api-documentation/).

## Installation

You can install idmc from CRAN:

```r
install.packages("idmc")
```

Alternatively, you can install the development version of idmc from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("OCHA-DAP/idmc")
```

## API URL

You need an IDMC endpoint URL to access the API. These are provided by
IDMC. The easiest way to save the URL for use in your R sessions is by
using `usethis::edit_r_environ()` and adding the variable there as:

```
IDMC_API="Insert API URL here"
```

## Usage

```{r child="vignettes/idmc-usage.Rmd"}
```
