---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# idmc

<!-- badges: start -->
  [![R-CMD-check](https://github.com/caldwellst/idmc/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/caldwellst/idmc/actions/workflows/R-CMD-check.yaml)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The goal of idmc is to provide easy access and wrangling of displacement data
stored in the
[Internal Displacement Monitoring Centre's](https://www.internal-displacement.org)
displacement database. The data is retrieved from the 
[Internal Displacement Update API](https://www.internal-displacement.org/sites/default/files/IDMC_IDU_API_Codebook_14102020.pdf).

## Installation

You can install the development version of idmc from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ocha-dap/idmc")
```


## Usage

```{r child="vignettes/idmc-usage.Rmd"}
```
## API URL

You need an API endpoint URL saved to your environment. These are provided by
IDMC. The easiest way to save the URL for use in your R sessions is by
using `usethis::edit_r_environ()` and adding the variable there as:

```
IDMC_API="Insert API URL here"
```

## Memoisation

`idmc_get_data()`, the function that requests to the IDU API, has cached
functionality based on `memoise::memeoise()` so that calls to the
`idmc_get_data()` function are cached in your local memory in a single session.
This means that once you've made a call to retrieve the displacement data from,
the API, running an identical request will use the cached data rather than
re-request the data from the IDU database.

If you need to ensure that the idmc package is making new requests to the API
each time `idmc_get_data()` is called, then
you will need to run `memoise::forget(idmc::idmc_get_data)` to clear the cache
prior to repeating a call. See the documentation of the
[memoise package](https://github.com/r-lib/memoise) for more details.
