---
title: "Usage"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Usage}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
api_envvar_available <- !is.na(Sys.getenv("IDMC_API", unset = NA))
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = api_envvar_available
)
```
  
```{r eval = !api_envvar_available, echo = FALSE, comment = NA}
message("`IDMC_API` env variable not set, so code chunks will not be evaluated.")  
```

```{r setup}
library(idmc)
```

The simple use for the `idmc` package is to retrieve the data from the
API directly into R.

```{r api}
df <- idmc_get_data()
df
```

This data frame, with variables described in the
[API documentation](https://www.internal-displacement.org/database/api-documentation/), includes 1 row per event.
We can normalize this to daily displacement, assuming uniform distribution of displacement
between start and end date, for all countries and type of displacement.
`idmc_transform_daily()`.

```{r transform}
idmc_transform_daily(df)
```

While there are a few other parameters you can play around with in these functions,
this is the primary purpose of this simple package.
