---
title: "Usage"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Usage}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(idmc)
```

The simplest use case for the `idmc` package is to retrieve the data from the
API directly into R.

```{r api}
df <- idmc_get_data()
df
```

This data frame, with variables described in the
[API documentation](https://www.internal-displacement.org/sites/default/files/IDMC_IDU_API_Codebook_14102020.pdf), includes 1 row per event. To generate daily displacement data across
all events for a country and type of displacement, we can use
`idmc_transform_daily()`.

```{r transform}
df_daily <- idmc_transform_daily(df)
df_daily
```

We can also generate displacement aggregates across time, such as weekly or
yearly simply using `idmc_rolling_sum()`.

```{r rolling}
df_rolling <- idmc_rolling_sum(df_daily)
df_rolling
```

Last, part of the use of this data is to flag abnormal levels of displacement.
These flags are generated through `idmc_flagging()` and the function is
also made available for other interested users. However, note that these flags
are under development and simply meant to be indicative of potential anomalies.

```{r flagging}
df_flagging <- idmc_flagging(df_rolling)
df_flagging
```
